---
title: "HW5"
author: "CC"
date: "11/6/2019"
output: github_document
---

# Problem 1: Iris Missing Data

For numeric variables (Sepal.Length, Sepal.Width, Petal.Length, and Petal.Width), fill in missing values with the mean of non-missing values. For the character variable (Species) replace the missing values with "virginica". Use a map statement.

## Loading Dataset
```{r}
library(tidyverse)

set.seed(10)
iris_with_missing = iris %>%
  map_df(~replace(.x, sample(1:150,20), NA)) %>%
  mutate(Species = as.character(Species))
```

## Cleaning dataset names and trying map statement

```{r}
im = 
iris_with_missing %>%
  janitor::clean_names()

#l = list(pull(im, sepal_length),
#        pull(im, sepal_width),
#        pull(im, petal_length),
#        pull(im, petal_width),
#        pull(im, species))

#l[[2]]


#meanf = function(x) {
#  if (!is.numeric(x)) {
#    stop("Argument x should be numeric")
#  } else if (length(x) == 1) {
#    stop("Cannot be computed for length 1 vectors")
#  }

#mean_x = mean(x)

#tibble(
#  sepal_length = mean(sepal_length),
#  sepal_width = mean(sepal_width),
#  petal_length = mean(petal_length),
#  petal_width = mean(petal_width),
#  species
#  )
#}

#meanf(iris_with_missing[[l]])

#output = map(iris_with_missing, mean)
```

## Different Method

Filling in missing values with a different method. Using summary(im) showed that the mean values for the numeric values were as follows: sepal_length = 5.819, sepal_width = 3.075, petal_length = 3.765, and petal_width = 1.192. Replace individually and recheck summary to ensure NAs no longer present.
```{r}
summary(im)

im$sepal_length <- replace_na(im$sepal_length, 5.819)
im$sepal_width <- replace_na(im$sepal_width, 3.075)
im$petal_length <- replace_na(im$petal_length, 3.765)
im$petal_width <- replace_na(im$petal_width, 1.192)
im$species <- replace_na(im$species, "virginica")

summary(im)
```

# Problem 2: Longitudinal Study

```{r}
list.files(path = "./data/")
```


# Problem 3: Regression

Running a model when beta1 = 0
```{r}
# Set design elements:
set.seed(1)
n=30

sim_regression = function(n, beta0 = 2, beta1 = 0) {
  
  sim_data = tibble(
    x = rnorm(n, mean = 1, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, 1)
  )
  
  ls_fit = lm(y ~ x, data = sim_data)
  
  broom::tidy(ls_fit)
  
  tibble(
    beta0_hat = coef(ls_fit)[1],
    beta1_hat = coef(ls_fit)[2]
  )
}

output = vector("list", 10000)

for (i in 1:10000) {
  output[[i]] = sim_regression(30)
}

sim_results = bind_rows(output)

sim_results = 
  rerun(10000, sim_regression(30, 2, 7.07)) %>% 
  bind_rows()

sim_results %>% 
  ggplot(aes(x = beta0_hat, y = beta1_hat)) + 
  geom_point()

sim_results %>% 
  pivot_longer(
    beta0_hat:beta1_hat,
    names_to = "parameter", 
    values_to = "estimate") %>% 
  group_by(parameter) %>% 
  summarize(emp_mean = mean(estimate),
            emp_var = var(estimate)) %>% 
  knitr::kable(digits = 3)
```

## Repeating regression

